Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-05 ms.tex
clarify definitions of model 1 and model 2 in the text
fixed weird table issue, more on Planck vs. FIRAS global parameters

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
\enddata
\end{deluxetable}

@@

Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
strong covariances, but even so several conclusions are clear: (1) a lower 
value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
(3). Because

>>>>

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & \PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
\enddata
\end{deluxetable}

% would be great to have uncertainties on each parameter as well (in the
% Planck case at least...) !!!!!!!!!!!!!!!

@@

Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
strong covariances, but even so several conclusions are clear: (1) a lower 
value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
is effectively identical to that found by FDS99 to within uncertainties and (3)
a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
strongly covariant with $\beta_1$, the difference of $f_1$ between the 
\PLANCK~and FIRAS best fits is not particularly significant.

% actually quantitatively assess, for a typical temperature (and frequency?)
% how the new f_1 value basically balances out the change in beta_1 ???

The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
separately for both model 1 (FIRAS+\IRAS) and model 2 (\PLANCK+\IRAS), each
defined by their respective global parameters listed in Table \ref{tab:global}.
